Conservation of interaction partners between related plants varies widely across communities and between plant families.

### 2019-02-20 manuscript/phylogenetic_signal_manuscript.tex
I think I shan't redo the within-family stuff after all

Supporting information: 1 file containing 4 sections.

@@

  We studied tested for phylogenetic signal in niche overlap within a 
  set of 59 pollination and 11 herbivory networks. These networks span 
  a range of biomes (desert to scrub forest to grassland) and 
  countries (Sweden to Australia). The herbivory networks included a 
  variety of types of herbivores but were dominated by insects 
  consuming leaves. To ensure that we were analysing interactions 
  influenced by similar sets of traits across networks, we restricted 
  our herbivory networks to insects consuming leaves and excluded 
  sap-sucking, leaf-mining, and galling insects as well as seed 
  predators and xylophagous insects; all of these interactions involve 
  different plant tissues and means of feeding than leaf consumption 
  and so may be influenced by different plant and insect traits. 
  Specifically, we removed any non-leaf consuming insects and any 
  plants which had no interaction partners after removing other types  
  of herbivores. The adjusted networks range in size between 19 and 
  997 total species (mean=162, median=97) with  between 8 and 132 
  plant species (mean=39.1, median=29.5). See \emph{Table S1, 
  Supporting Information} [[NOT DONE!]]for details on the original sources of all 
  networks.

@@

  % [[It appears we switched to Jaccard and Sorenson dissimilarities - number of shared partners and number of shared partners*2/notshared.]]

\subsection*{Statistical analysis}

  We modelled the relationship between niche overlap and phylogenetic distance
  using a logistic regression. We used both the numbers of shared ($M_{ij}$)and 
  non-shared ($U_{ij}$) partners as dependent variables and centred, scaled phylogenetic 
  distance as the independent variable. This approach is conceptually similar to 
  modelling successes and failures in a binomial-distributed process. 
  Accordingly, we assumed a binomial distribution for residuals. Regressions of
  niche overlap and phylogenetic distance within each network were fit using the
  R~\citep{R} base function ``glm''. These separate regressions avoid the potential
  for confounding the effects of different relationships in different networks. As
  we also wished to evaluate the overall trend across networks, we fit an additional
  regression of niche overlap and phylogenetic distance across all network types.
  As well as the fixed effect of phylogenetic distance, this regression included 
  fixed effects of network type (pollination or herbivory) and the interaction 
  between phylogenetic network type and random intercepts and slopes per network.
  This expanded regression was fit using the R~\citep{R} function ``glmer'' from
  package \emph{lme4}~\citep{lme4}. [[Confirm that I actually use the separate 
  regressions and not just the full one. ]]

@@

    Taking all families together, the probability of species in the same family sharing interaction partners decreased wiht increasing phylogenetic distance in both plant-pollinator and plant-herbivore networks and the strength of this relationship did not differ significantly between network types ($\beta_{distance}$=-4.75, $p$=0.012; $\beta_{distance:PH}$=-1.73, $p$=0.681). Plants in plant-herbivore networks had a higher probability of sharing interaction partners with a member of the same family ($\beta_{PH}$=0.78, $p$=0.007).

@@

    For the families
    that were well represented in pollination networks, overlap decreased
    with increasing phylogenetic distance in 18 (Table~\ref{family_slopes_pp}).
    There was no significant relationship between overlap and phylogenetic distance in
    a further 15 plant families. Finally, the overlap between pairs of \emph{Polygonaceae}
    increased with increasing phylogenetic distance. 
    Of the seven plant families that were sufficiently well represented in herbivory 
    networks, overlap decreased with increasing phylogenetic distance in four 
    (Table~\ref{family_slopes_ph}; Fig.~\ref{within_family_regression}). Two
    families did not show significant relationships between phylogenetic distance and overlap,
    and in one family, \emph{Fabaceae}, overlap of interaction partners increased with 
    increasing phylogenetic distance.

@@

  \begin{table}[!h]
  \caption{\small Change in log odds (per million years of phylogenetic distance) of a pair of plants in the same family sharing a herbivore.}
  \label{family_slopes_ph}
  \begin{tabular}{|l  rr|}
  \hline
    Family & Change in log odds & $P$-value \\
    \hline
    \emph{Asteraceae} & -1.73 &  0.550 \\
    \emph{Euphorbiaceae} & -19.2 & \textbf{\textless0.001} \\
    \emph{Fabaceae} & 18.7 &  \textbf{0.046} \\
    \emph{Melastomataceae} & -13.2 & \textbf{0.022} \\
    \emph{Moraceae} & -2.13 & 0.092 \\
    \emph{Nothofagaceae} & -595 & \textgreater{0.999} \\
    \emph{Pinaceae} &  -25.8 & 0.733 \\
    \emph{Poaceae} & -4.50 & \textbf{0.020} \\
    \emph{Rubiaceae} & -8.16 &  \textbf{0.006} \\
  \hline
  \end{tabular}
  \smallskip
  \footnotesize

@@

  \begin{table}[!h]
  \caption{
  \small Change in log odds (per million years of phylogenetic distance) of a pair of plants in the same family sharing a pollinator.}
  \small
  \label{family_slopes_pp}
  \begin{tabular}{|l  rr|}
    \hline
    Family  & Change in log odds & $P$-value \\
    \hline
    \emph{Adoxaceae} &  -65.8 & 0.163 \\
    \emph{Amaryllidaceae} &  -17.9 & \textbf{0.015} \\
    \emph{Apiaceae} &  10.9  & \textbf{0.006} \\
    \emph{Apocynaceae} &  -6.96  & \textbf{0.037} \\
    \emph{Asparagaceae} &  -6.23  & 0.189 \\
    \emph{Asteraceae}* &  -1.47  & \textbf{\textless0.001} \\
    \emph{Berberidaceae} &  -1.48$\times10^3$ & \textgreater0.999 \\
    \emph{Boraginaceae} &  -5.15  & \textbf{\textless0.001} \\
    \emph{Brassicaceae} &  -11.2 & 0.072 \\
    \emph{Calceolariaceae} &  156 & 0.998 \\
    \emph{Campanulaceae} &  334 & 0.999 \\
    \emph{Caprifoliaceae} &  0.310 & 0.959 \\
    \emph{Caryophyllaceae} &  2.09 & 0.644 \\
    \emph{Cistaceae} &  -11.4 & \textbf{\textless0.001} \\
    \emph{Convolvulaceae} &  -1.84  & 0.837 \\
    \emph{Ericaceae} &  4.61 & 0.116 \\
    \emph{Fabaceae}* &  -12.9 & \textbf{\textless0.001} \\
    \emph{Geraniaceae} &  -3.31  & 0.624 \\
    \emph{Hydrangeaceae} &  0.057 & 0.982 \\
    \emph{Iridaceae} &  -27.9 & 0.078 \\
    \emph{Lamiaceae} &  -5.01  & \textbf{\textless0.001} \\
    \emph{Loasaceae} &  -865  & \textgreater0.999 \\
    \emph{Malpighiaceae} &  2.80 & 0.168 \\
    \emph{Malvaceae} &  -5.56  & 0.363 \\
    \emph{Melastomataceae}* &  5.19 & 0.577 \\
    \emph{Montiaceae} &  -1.12  & 0.870 \\
    \emph{Myrtaceae} &  8.55 & 0.071 \\
    \emph{Oleaceae} &  0.995 & 0.855 \\
    \emph{Onagraceae} &  -556  & \textgreater0.999 \\
    \emph{Orchidaceae} &  -14.5 & 0.145 \\
    \emph{Orobanchaceae} &  24.2  & 0.326 \\
    \emph{Papaveraceae} &  -11.2 & 0.511 \\
    \emph{Phyllanthaceae} &  9.99 & 0.433 \\
    \emph{Plantaginaceae} &  -8.48  & \textbf{0.001} \\
    \emph{Poaceae}* &  69.2  & \textbf{0.003} \\
    \emph{Polygonaceae} &  -14.8 & \textbf{\textless0.001} \\
    \emph{Primulaceae} &  14.9  & 0.343 \\
    \emph{Ranunculaceae} &  -38.0 & \textbf{\textless0.001} \\
    \emph{Rosaceae} &  0.759 & 0.735 \\
    \emph{Rubiaceae}* &  -13.0 & \textbf{0.026} \\
    \emph{Salicaceae} &  -1.90  & 0.545 \\
    \emph{Sapindaceae} &  821 & 0.999 \\
    \emph{Saxifragaceae} &  -0.092  & 0.992 \\
    \emph{Solanaceae} &  -21.9 & 0.189 \\
    \emph{Tropaeolaceae} &  192 & 0.997 \\
    \emph{Verbenaceae} &  -9.03  & 0.627 \\
    \emph{Violaceae} &  -0.487  & 0.974 \\
  \hline
  \end{tabular}
  \smallskip
  \footnotesize

>>>>

Supporting information: 1 file containing 1 section.

@@

  We studied tested for phylogenetic signal in niche overlap within a 
  set of 59 pollination and 11 herbivory networks. These networks span 
  a range of biomes (desert to scrub forest to grassland) and 
  countries (Sweden to Australia). The herbivory networks included a 
  variety of types of herbivores but were dominated by insects 
  consuming leaves. To ensure that we were analysing interactions 
  influenced by similar sets of traits across networks, we restricted 
  our herbivory networks to insects consuming leaves and excluded 
  sap-sucking, leaf-mining, and galling insects as well as seed 
  predators and xylophagous insects; all of these interactions involve 
  different plant tissues and means of feeding than leaf consumption 
  and so may be influenced by different plant and insect traits. 
  Specifically, we removed any non-leaf consuming insects and any 
  plants which had no interaction partners after removing other types  
  of herbivores. The adjusted networks range in size between 19 and 
  997 total species (mean=162, median=97) with  between 8 and 132 
  plant species (mean=39.1, median=29.5). See \emph{Table S1, 
  Supporting Information} for details on the original sources of all 
  networks.

@@

  % [[It appears we switched to Jaccard and Sorenson dissimilarities - number of shared partners and number of shared partners*2/notshared.]]
\subsection*{Statistical analysis}

  We modelled the relationship between nich

e overlap and phylogenetic distance
  using a logistic regression. We used both the numbers of shared ($M_{ij}$)and 
  non-shared ($U_{ij}$) partners as dependent variables and centred, scaled phylogenetic 
  distance as the independent variable. This approach is conceptually similar to 
  modelling successes and failures in a binomial-distributed process. 
  Accordingly, we assumed a binomial distribution for residuals. Regressions of
  niche overlap and phylogenetic distance within each network were fit using the
  R~\citep{R} base function ``glm''. These separate regressions avoid the potential
  for confounding the effects of different relationships in different networks. As
  we also wished to evaluate the overall trend across networks, we fit an additional
  regression of niche overlap and phylogenetic distance across all network types.
  As well as the fixed effect of phylogenetic distance, this regression included 
  fixed effects of network type (pollination or herbivory) and the interaction 
  between phylogenetic network type and random intercepts and slopes per network.
  This expanded regression was fit using the R~\citep{R} function ``glmer'' from
  package \emph{lme4}~\citep{lme4}.

@@

  % Regression of all families at once with RE's for network
    Taking all families together, the probability of species in the same family sharing interaction partners decreased wiht increasing phylogenetic distance in both plant-pollinator and plant-herbivore networks and the strength of this relationship did not differ significantly between network types ($\beta_{distance}$=-4.75, $p$=0.012; $\beta_{distance:PH}$=-1.73, $p$=0.681). Plants in plant-herbivore networks had a higher probability of sharing interaction partners with a member of the same family ($\beta_{PH}$=0.78, $p$=0.007).

@@

    % Regressions for each family separately.
    For the families
    that were well represented in pollination networks, overlap decreased
    with increasing phylogenetic distance in 18 (Table~\ref{family_slopes_pp}).
    There was no significant relationship between overlap and phylogenetic distance in
    a further 15 plant families. Finally, the overlap between pairs of \emph{Polygonaceae}
    increased with increasing phylogenetic distance. 
    Of the seven plant families that were sufficiently well represented in herbivory 
    networks, overlap decreased with increasing phylogenetic distance in four 
    (Table~\ref{family_slopes_ph}; Fig.~\ref{within_family_regression}). Two
    families did not show significant relationships between phylogenetic distance and overlap,
    and in one family, \emph{Fabaceae}, overlap of interaction partners increased with 
    increasing phylogenetic distance.

@@

  \begin{table}[!h]
  \caption{\small Change in log odds (per million years of phylogenetic distance) of a pair of plants in the same family sharing a herbivore.}
  % These are from the regressions within each family. P-vals need to be replaced, to come from randomizations. Coefficients should be fine.
  \label{family_slopes_ph}
  \begin{tabular}{|l  rr|}
  \hline
    Family & Change in log odds & $P$-value \\
    \hline
    \emph{Asteraceae} & -1.73 &  0.550 \\
    \emph{Euphorbiaceae} & -19.2 & \textbf{\textless0.001} \\
    \emph{Fabaceae} & 18.7 &  \textbf{0.046} \\
    \emph{Melastomataceae} & -13.2 & \textbf{0.022} \\
    \emph{Moraceae} & -2.13 & 0.092 \\
    \emph{Nothofagaceae} & -595 & \textgreater{0.999} \\
    \emph{Pinaceae} &  -25.8 & 0.733 \\
    \emph{Poaceae} & -4.50 & \textbf{0.020} \\
    \emph{Rubiaceae} & -8.16 &  \textbf{0.006} \\
  \hline
  \end{tabular}
  \smallskip
  \footnotesize

@@

  \begin{table}[!h]
  \caption{
  \small Change in log odds (per million years of phylogenetic distance) of a pair of plants in the same family sharing a pollinator.}
  % These are from the regressions within each family. P-vals need to be replaced, to come from randomizations. Coefficients should be fine.
  \small
  \label{family_slopes_pp}
  \begin{tabular}{|l  rr|}
    \hline
    Family  & Change in log odds & $P$-value \\
    \hline
    \emph{Adoxaceae} &  -65.8 & 0.163 \\
    \emph{Amaryllidaceae} &  -17.9 & \textbf{0.015} \\
    \emph{Apiaceae} &  10.9  & \textbf{0.006} \\
    \emph{Apocynaceae} &  -6.96  & \textbf{0.037} \\
    \emph{Asparagaceae} &  -6.23  & 0.189 \\
    \emph{Asteraceae}* &  -1.47  & \textbf{\textless0.001} \\
    \emph{Berberidaceae} &  -1.48$\times10^3$ & \textgreater0.999 \\
    \emph{Boraginaceae} &  -5.15  & \textbf{\textless0.001} \\
    \emph{Brassicaceae} &  -11.2 & 0.072 \\
    \emph{Calceolariaceae} &  156 & 0.998 \\
    \emph{Campanulaceae} &  334 & 0.999 \\
    \emph{Caprifoliaceae} &  0.310 & 0.959 \\
    \emph{Caryophyllaceae} &  2.09 & 0.644 \\
    \emph{Cistaceae} &  -11.4 & \textbf{\textless0.001} \\
    \emph{Convolvulaceae} &  -1.84  & 0.837 \\
    \emph{Ericaceae} &  4.61 & 0.116 \\
    \emph{Fabaceae}* &  -12.9 & \textbf{\textless0.001} \\
    \emph{Geraniaceae} &  -3.31  & 0.624 \\
    \emph{Hydrangeaceae} &  0.057 & 0.982 \\
    \emph{Iridaceae} &  -27.9 & 0.078 \\
    \emph{Lamiaceae} &  -5.01  & \textbf{\textless0.001} \\
    \emph{Loasaceae} &  -865  & \textgreater0.999 \\
    \emph{Malpighiaceae} &  2.80 & 0.168 \\
    \emph{Malvaceae} &  -5.56  & 0.363 \\
    \emph{Melastomataceae}* &  5.19 & 0.577 \\
    \emph{Montiaceae} &  -1.12  & 0.870 \\
    \emph{Myrtaceae} &  8.55 & 0.071 \\
    \emph{Oleaceae} &  0.995 & 0.855 \\
    \emph{Onagraceae} &  -556  & \textgreater0.999 \\
    \emph{Orchidaceae} &  -14.5 & 0.145 \\
    \emph{Orobanchaceae} &  24.2  & 0.326 \\
    \emph{Papaveraceae} &  -11.2 & 0.511 \\
    \emph{Phyllanthaceae} &  9.99 & 0.433 \\
    \emph{Plantaginaceae} &  -8.48  & \textbf{0.001} \\
    \emph{Poaceae}* &  69.2  & \textbf{0.003} \\
    \emph{Polygonaceae} &  -14.8 & \textbf{\textless0.001} \\
    \emph{Primulaceae} &  14.9  & 0.343 \\
    \emph{Ranunculaceae} &  -38.0 & \textbf{\textless0.001} \\
    \emph{Rosaceae} &  0.759 & 0.735 \\
    \emph{Rubiaceae}* &  -13.0 & \textbf{0.026} \\
    \emph{Salicaceae} &  -1.90  & 0.545 \\
    \emph{Sapindaceae} &  821 & 0.999 \\
    \emph{Saxifragaceae} &  -0.092  & 0.992 \\
    \emph{Solanaceae} &  -21.9 & 0.189 \\
    \emph{Tropaeolaceae} &  192 & 0.997 \\
    \emph{Verbenaceae} &  -9.03  & 0.627 \\
    \emph{Violaceae} &  -0.487  & 0.974 \\
  \hline
  \end{tabular}
  \smallskip
  \footnotesize
